An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-05 EconGrowth2.Rnw
Edited text to create 95% CI graphs and tables for different CES nestings.

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have tables for all nestings. ****

@@

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have tables for all nestings. ****

<<CESq_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="Q")
printCESParamsTableB(energyType="Q")
@

<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q")
@

>>>>

The 95\% confidence intervals associated 
with Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} 
and \ref{fig:CES_sigma_1_delta_1_Scatter_Graph}
are shown in Tables~\ref{tab:CES_Parameters_A} 
and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.

@@

The 95\% confidence intervals associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
**** Ensure that we have figures for all nestings. ****

<<CESq_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="Q", nest="(kl)e")
printCESParamsTableB(energyType="Q", nest="(kl)e")
@

<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q", nest="(kl)e")
@
